Kids home characteristics/activity summary

### 2020-03-26 home_char_act_summary.Rmd
data cleaning/merging updates

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 16 March 2020"
output:
  pdf_document: default
  powerpoint_presentation: default
  word_document: default
---

@@

```{r}
# Load dataset
home_char_clean <- read_rds("Output/home_char_clean.rds") %>% 
  mutate(chimney_clean = factor(chimney_clean,
                                levels = c("Less than 6 months ago",
                                           "6-12 months ago", "12-18 months ago",
                                           "More than 18 months ago"),
                                labels = c("< 6 months ago",
                                           "6-12 months ago", "12-18 months ago",
                                           "> 18 months ago")),
         stove_age = factor(stove_age,
                            levels = c("0-5 years old", "6-10 years old",
                                       "11-15 years old", "16 + years old",
                                       "Do not know")))

home_act_clean <- read_rds("Output/home_act_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

@@

@@

```{r, fig.height=8}
home_char_plot <- home_char_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, residents_smoke, residents_smoke_inside, home_damp:home_insert) %>% 
  pivot_longer(cols = c("residents_smoke":"home_insert"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, ncol = 2)
home_char_plot
```

```{r}
home_char_function <- function(data, variable) {

home_plot <- data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
home_plot

@@

home_char_function(home_char_clean, "residents_total")
home_char_function(home_char_clean, "residents_under5")
home_char_function(home_char_clean, "residents_under18")
home_char_function(home_char_clean, "residents_smoke")
home_char_function(home_char_clean, "residents_smoke_inside")
home_char_function(home_char_clean, "home_type")
home_char_function(home_char_clean, "home_floors")
home_char_function(home_char_clean, "home_windows")
home_char_function(home_char_clean, "home_bedrooms")
home_char_function(home_char_clean, "home_pets")
home_char_function(home_char_clean, "home_furry")
home_char_function(home_char_clean, "primary_heat")
home_char_function(home_char_clean, "secondary_heat")
home_char_function(home_char_clean, "stove_age")
home_char_function(home_char_clean, "stove_cert")
home_char_function(home_char_clean, "chimney_clean")
home_char_function(home_char_clean, "home_mold")
home_char_function(home_char_clean, "home_damp")
home_char_function(home_char_clean, "home_fireplace")
home_char_function(home_char_clean, "home_furnace")
home_char_function(home_char_clean, "home_woodstove")
home_char_function(home_char_clean, "home_insert")
```

```{r, fig.height=8}
home_act_plot <- home_act_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home_act_gas:home_act_sweep) %>% 
  pivot_longer(cols = c("home_act_gas":"home_act_sweep"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, ncol = 2)
home_act_plot
```

```{r}
home_act_function <- function(data, variable) {

home_plot <- data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
home_plot

@@

home_act_function(home_act_clean, "home_act_gas")
home_act_function(home_act_clean, "home_act_elect")
home_act_function(home_act_clean, "home_act_propane")
home_act_function(home_act_clean, "home_act_oil")
home_act_function(home_act_clean, "home_act_smoking")
home_act_function(home_act_clean, "home_act_incense")
home_act_function(home_act_clean, "home_act_candle")
home_act_function(home_act_clean, "home_act_kerosene")
home_act_function(home_act_clean, "home_act_windows")
home_act_function(home_act_clean, "home_act_door")
home_act_function(home_act_clean, "home_act_sweep")
```

```{r, include=FALSE}
#### Abstract/manuscript tables ####

@@

```{r, include=FALSE}
# Summarize numeric vars
kids_char <- home_char_filtered %>%  
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(home_furry, na.rm = TRUE), 
            "SD" = sd(home_furry, na.rm = TRUE),
            "min" = min(home_furry, na.rm = TRUE), 
            "max" = max(home_furry, na.rm = TRUE))
kable(kids_char, digits = 1, align = "c")

>>>>

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 25 March 2020"
output:
  pdf_document: default
  powerpoint_presentation: default
---

@@

```{r}
# Load dataset
home_char_clean <- read_rds("Output/home_char_clean.rds") 
home_act_clean <- read_rds("Output/home_act_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
#pm_clean <- read_rds("Output/pm_clean.rds")
```

@@

```{r}
table(home_char_clean$primary_heat, home_char_clean$secondary_heat, home_char_clean$area,
      dnn = c("primary heating", "secondary heating", "area"))
```

@@

```{r}
home_char_filtered <- read_rds("Output/home_char_clean.rds") %>% 
  mutate(chimney_clean = factor(chimney_clean,
                                levels = c("Less than 6 months ago",
                                           "6-12 months ago", "12-18 months ago",
                                           "More than 18 months ago"),
                                labels = c("< 6 months ago",
                                           "6-12 months ago", "12-18 months ago",
                                           "> 18 months ago")),
         stove_age = factor(stove_age,
                            levels = c("0-5 years old", "6-10 years old",
                                       "11-15 years old", "16 + years old",
                                       "Do not know")))
```

```{r, fig.height=8}
home_char_plot <- home_char_filtered %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, residents_smoke, residents_smoke_inside, home_damp:home_insert) %>% 
  pivot_longer(cols = c("residents_smoke":"home_insert"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, ncol = 2) +
    scale_fill_manual(values = jv_palette)
home_char_plot
```

```{r}
home_char_function <- function(data, var, title_label, y_label) {

  home_char_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 20, colour = "black"),
          legend.text = element_text(size = 18, colour = "black"),
          legend.title = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  home_char_plot

@@

home_char_function(home_char_filtered, "residents_smoke", "Residents smoke", "count")
home_char_function(home_char_filtered, "residents_smoke_inside", "Residents smoke inside", "count")
home_char_function(home_char_filtered, "home_type", "Home type", "count")
home_char_function(home_char_filtered, "home_floors", "Floors in home", "count")
home_char_function(home_char_filtered, "home_windows", "Windows in home", "count")
home_char_function(home_char_filtered, "home_bedrooms", "Bedrooms in home", "count")
home_char_function(home_char_filtered, "home_pets", "Pets in home", "count")
home_char_function(home_char_filtered, "home_furry", "Furry pet in home", "count")
home_char_function(home_char_filtered, "primary_heat", "Primary heat", "count")
home_char_function(home_char_filtered, "secondary_heat", "Secondary heat", "count")
home_char_function(home_char_filtered, "stove_age", "Stove age", "count")
home_char_function(home_char_filtered, "stove_cert", "Stove EPA certified", "count")
home_char_function(home_char_filtered, "chimney_clean", "Chimney last cleaned", "count")
home_char_function(home_char_filtered, "home_mold", "Home mold", "count")
home_char_function(home_char_filtered, "home_damp", "Home damp", "count")
home_char_function(home_char_filtered, "home_fireplace", "Home fireplace", "count")
home_char_function(home_char_filtered, "home_furnace", "Home furnace", "count")
```

```{r, fig.height=8}
home_act_plot <- home_act_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home_act_gas:home_act_sweep) %>% 
  pivot_longer(cols = c("home_act_gas":"home_act_sweep"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, ncol = 2) +
    scale_fill_manual(values = jv_palette)
home_act_plot
```

```{r}
home_act_function <- function(data, var, title_label, y_label) {

  home_act_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 20, colour = "black"),
          legend.text = element_text(size = 18, colour = "black"),
          legend.title = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  home_act_plot

@@

home_act_function(home_act_clean, "home_act_gas", "Gas appliance used", "count")
home_act_function(home_act_clean, "home_act_elect", "Electric appliance used", "count")
home_act_function(home_act_clean, "home_act_propane", "Propane appliance used", "count")
home_act_function(home_act_clean, "home_act_oil", "Oil appliance used", "count")
home_act_function(home_act_clean, "home_act_smoking", "Smoking in home", "count")
home_act_function(home_act_clean, "home_act_incense", "Incense burned", "count")
home_act_function(home_act_clean, "home_act_candle", "Candle burned", "count")
home_act_function(home_act_clean, "home_act_kerosene", "Kerosene burned", "count")
home_act_function(home_act_clean, "home_act_windows", "Windows open", "count")
home_act_function(home_act_clean, "home_act_door", "Doors open", "count")
home_act_function(home_act_clean, "home_act_sweep", "Sweeping/cleaning/vacuuming", "count")
```

```{r, include=FALSE, eval=FALSE}
#### Abstract/manuscript tables ####

@@

```{r, include=FALSE, eval=FALSE}
# Summarize numeric vars
kids_char <- home_char_filtered %>%  
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(home_furry, na.rm = TRUE), 
            "SD" = sd(home_furry, na.rm = TRUE),
            "min" = min(home_furry, na.rm = TRUE), 
            "max" = max(home_furry, na.rm = TRUE))
kable(kids_char, digits = 1, align = "c")
